---
title: "SRA Characterization"
author: "Edward Richards"
date: "16 June 2017"
output: word_document

---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## SRA Datasets: 
## Platform Summary 
### Table, Barplot & Line Graph

Table 1 details how many times a specific sequencing platform was used by a dataset present on the SRA. Figure 1 is a barplot which represents this information. The number of datasets which did not provide which platform was used is also included in both the table and the figure (NA). Figure 2 is a line graph which represents the number of bases sequenced by each platform per year (not cumulative).


```{r echo = FALSE}
#Platform table table
library(knitr)
kable(df[1:14,], caption = "Table 1: Platform Counts Table", col.names=c("Platform", "Frequency"))
```

```{r img-setup,df,fig.height = 7, fig.width = 10, fig.align = "center", echo=FALSE,results='hide',cache=FALSE,warning=FALSE}
#Create platforms barplot
p<-ggplot(data=df, aes(x=df$Platform, y=len)) +
  geom_bar(aes(fill=Platform),stat="identity")+ scale_y_log10() +
  scale_x_discrete(labels=xLabs)

#Add labels
p <- p + labs(x = "Platform")
p <- p + labs(y = "Count (log10)")
p <- p + labs(title = "Fig. 1: Number of Datasets Submitted to SRA vs Platform Used")
p <- p + labs(colour = "Platforms") 
p

#Linegraph
platPlot <- ggplot(data=lineDF, aes(x=lineDF$Year, y=lineDF$Bases, group=lineDF$Platform)) +
  geom_line(aes(color=lineDF$Platform))+ scale_y_log10() +
  geom_point(aes(color=lineDF$Platform))

#Add labels to line graph
platPlot <- platPlot + labs(x = "Year")
platPlot <- platPlot + labs(y = "Bases (log10)")
platPlot <- platPlot + labs(title = "Fig. 2: Number of Bases Sequenced by Each Platform per Year")
platPlot <- platPlot + labs(colour = "Platforms") 
platPlot
```

## Organism Summary 
### Table & Barplots

Table 2 details organisms used by all datasets present on the SRA. Figures 3 & 4 represent this information, however, figure 4 does not include Homo sapiens and Mus musculus, and does away with the log scale on the y-axis. Datasets which did not include which organism was used were not included. All latin names correlate with NCBI taxonomic IDs.
```{r echo = FALSE}
#Organism table
library(knitr)
kable(orgCounts[1:20,], caption = "Table 2: Organism Counts Table", col.names=c("Taxonomic Name", "Frequency"))
```

```{r img-setup,fig.height = 7, fig.width = 10, fig.align = "center", echo=FALSE,results='hide',cache=FALSE,warning=FALSE,message=FALSE}

#Create organism plot
pOrg<-ggplot(data=dfOrg, aes(x=orgCounts$Scientific.Name, y=lenOrg)) +
  geom_bar(aes(fill=orgCounts$Scientific.Name),stat="identity") + scale_y_log10() +
  scale_x_discrete(labels=xLabsOrg)

#Add labels to plot
pOrg <- pOrg + labs(x = "Organism")
pOrg <- pOrg + labs(y = "Count (log10)")
pOrg <- pOrg + labs(title = "Fig. 3: Number of Datasets Submitted to SRA vs Organism Used")
pOrg <- pOrg + guides(fill=guide_legend(title="Organisms"))
pOrg

#Create organism plot without top two 
pOrgN<-ggplot(data=dfOrg, aes(x=orgCountsN$Scientific.Name, y=lenOrg)) +
  geom_bar(aes(fill=orgCountsN$Scientific.Name),stat="identity") +
  scale_x_discrete(labels=xLabsOrg)

#Add labels to plot
pOrgN <- pOrgN + labs(x = "Organism")
pOrgN <- pOrgN + labs(y = "Count")
pOrgN <- pOrgN + labs(title = "Fig 4: Number of Datasets Submitted to SRA vs Organism Used")
pOrgN <- pOrgN + guides(fill=guide_legend(title="Organisms"))
pOrgN
```

## Genus Rattus 
### Table & Word Cloud

Table 3 exhibits the total number of each species fallng under genus *Rattus* present on the SRA. Figure 5 is a word cloud exhibitng all metadata retrieved from the SRA which is associated with the genus *Rattus* datasets.
```{r echo = FALSE}
#Organism table
kable(ratDescCount[1:8,], caption = "Table 3: Genus Rattus Counts Table", col.names=c("Taxonomic Name", "Frequency"))

set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```
